---
title: "Data Analysing"
output: html_notebook
---

## Libries
```{r}
library(countrycode)
library(plyr)
library(ggplot2)
library(dplyr)

```

### Import Data set
```{r}
dataSet = read.csv("cleanedDataSet.csv")
head(dataSet)
```


# Distribution of employees by country

Since employee_residence data in ISO alpha 2 format, we have to convert it into standard country names.
after that we take frequency of countries.
```{r}
countryName = countrycode::countrycode(dataSet$employee_residence, "iso2c", "country.name")

countryFreq = plyr::count(countryName)
countryFreq
```

To plot these data first we use map_data in ggplot
```{r}
mapData = map_data("world")
mapData
```
Note that following countries has different names in *mapData*. Therefore we have to change these name.

```{r}
countryFreq$x[!(countryFreq$x %in% mapData$region)]
```
```{r}
countryFreq$x[countryFreq$x == "Bosnia & Herzegovina"] = "Bosnia and Herzegovina"
countryFreq$x[countryFreq$x == "Czechia"] = "Czech Republic"
countryFreq$x[countryFreq$x == "Hong Kong SAR China"] = "China"
countryFreq$x[countryFreq$x == "United Kingdom"] = "UK"
countryFreq$x[countryFreq$x == "United States"] = "USA"



countryFreq$x[!(countryFreq$x %in% mapData$region)]
colnames(countryFreq)[1] = "region"

countryFreq["logFreq"] = log10(countryFreq$freq)
countryFreq
```
Let's plot the data.

```{r warning=FALSE}

mapData = dplyr::left_join(mapData,countryFreq,by = "region")


ggplot(mapData,aes(mapData$long,mapData$lat,group=mapData$group))+
  geom_polygon(aes(fill = mapData$logFreq),color = "#373737")+
  scale_fill_gradient(low = "#d75ca2",high = "#410179",na.value = "#c0c0c2",breaks =c(0,1,2,3),labels = c("0","10","100","1000"),name = "")+
  labs(title = "Distribution of Employees by Country",x="",y="")+
  scale_x_continuous(labels = NULL)+
  scale_y_continuous(labels = NULL)+
  theme_linedraw()

```

## Distribution of Companies by Country


```{r}
companyLoc = countrycode::countrycode(dataSet$company_location, "iso2c", "country.name")

companyFreq = plyr::count(companyLoc)

mapData = map_data("world")

companyFreq$x[!(companyFreq$x %in% mapData$region)]

companyFreq$x[companyFreq$x == "Bosnia & Herzegovina"] = "Bosnia and Herzegovina"
companyFreq$x[companyFreq$x == "Czechia"] = "Czech Republic"
companyFreq$x[companyFreq$x == "Hong Kong SAR China"] = "China"
companyFreq$x[companyFreq$x == "United Kingdom"] = "UK"
companyFreq$x[companyFreq$x == "United States"] = "USA"



companyFreq$x[!(companyFreq$x %in% mapData$region)]
colnames(companyFreq)[1] = "region"

companyFreq["logFreq"] = log10(companyFreq$freq)

mapData = dplyr::left_join(mapData,companyFreq,by = "region")


ggplot(mapData,aes(mapData$long,mapData$lat,group=mapData$group))+
  geom_polygon(aes(fill = mapData$logFreq),color = "#373737")+
  scale_fill_gradient(low = "#67e26d",high = "#065064",na.value = "#c0c0c2",breaks =c(0,1,2,3),labels = c("0","10","100","1000"),name = "")+
  labs(title = "Distribution of Company by Country",x="",y="")+
  scale_x_continuous(labels = NULL)+
  scale_y_continuous(labels = NULL)+
  theme_linedraw()

```

