---
title: "Data Analysing"
output: html_notebook
---

## Libries
```{r}
library(countrycode)
library(plyr)
library(ggplot2)
library(dplyr)

```

### Import Data set
```{r}
dataSet = read.csv("cleanedDataSet.csv")
head(dataSet)
```


# Distribution of employees by country

Since employee_residence data in ISO alpha 2 format, we have to convert it into standard country names.
after that we take frequency of countries.
```{r}
countryName = countrycode::countrycode(dataSet$employee_residence, "iso2c", "country.name")

countryFreq = plyr::count(countryName)
countryFreq
```

To plot these data first we use map_data in ggplot
```{r}
mapData = map_data("world")
mapData
```
Note that following countries has different names in *mapData*. Therefore we have to change these name.

```{r}
countryFreq$x[!(countryFreq$x %in% mapData$region)]
```
```{r}
countryFreq$x[countryFreq$x == "Bosnia & Herzegovina"] = "Bosnia and Herzegovina"
countryFreq$x[countryFreq$x == "Czechia"] = "Czech Republic"
countryFreq$x[countryFreq$x == "Hong Kong SAR China"] = "China"
countryFreq$x[countryFreq$x == "United Kingdom"] = "UK"
countryFreq$x[countryFreq$x == "United States"] = "USA"



countryFreq$x[!(countryFreq$x %in% mapData$region)]
colnames(countryFreq)[1] = "region"

countryFreq["logFreq"] = log10(countryFreq$freq)
countryFreq
```
Let's plot the data.

```{r warning=FALSE}

mapData = dplyr::left_join(mapData,countryFreq,by = "region")


ggplot(mapData,aes(mapData$long,mapData$lat,group=mapData$group))+
  geom_polygon(aes(fill = mapData$logFreq),color = "#373737")+
  scale_fill_gradient(low = "#d75ca2",high = "#410179",na.value = "#c0c0c2",breaks =c(0,1,2,3),labels = c("0","10","100","1000"),name = "")+
  labs(title = "Distribution of Employees by Country",x="",y="")+
  scale_x_continuous(labels = NULL)+
  scale_y_continuous(labels = NULL)+
  theme(plot.title = element_text(size = 16,face = "bold"))+
  theme_linedraw()

```

## Distribution of Companies by Country


```{r}
companyLoc = countrycode::countrycode(dataSet$company_location, "iso2c", "country.name")

companyFreq = plyr::count(companyLoc)

mapData = map_data("world")

companyFreq$x[!(companyFreq$x %in% mapData$region)]

companyFreq$x[companyFreq$x == "Bosnia & Herzegovina"] = "Bosnia and Herzegovina"
companyFreq$x[companyFreq$x == "Czechia"] = "Czech Republic"
companyFreq$x[companyFreq$x == "Hong Kong SAR China"] = "China"
companyFreq$x[companyFreq$x == "United Kingdom"] = "UK"
companyFreq$x[companyFreq$x == "United States"] = "USA"



companyFreq$x[!(companyFreq$x %in% mapData$region)]
colnames(companyFreq)[1] = "region"

companyFreq["logFreq"] = log10(companyFreq$freq)

mapData = dplyr::left_join(mapData,companyFreq,by = "region")


ggplot(mapData,aes(long,lat,group=group))+
  geom_polygon(aes(fill = logFreq),color = "#373737")+
  scale_fill_gradient(low = "#67e26d",high = "#065064",na.value = "#c0c0c2",breaks =c(0,1,2,3),labels = c("0","10","100","1000"),name = "")+
  labs(title = "Distribution of Company by Country",x="",y="")+
  scale_x_continuous(labels = NULL)+
  scale_y_continuous(labels = NULL)+
  theme_linedraw()

```

### Most common Data Science related job field

```{r}
library(wordcloud2)
library(RColorBrewer)

cJobT = plyr::count(dataSet$job_title)

cJobT = cJobT[order(cJobT$freq,decreasing = T),]
cJobT = cJobT[1:100,]
cJobT["sqrtFreq"] = sqrt(cJobT$freq)
cJobT

set.seed(20000523)
wordcloud2(cJobT[c(1,3)],size = 0.5)

```
```{r}
library(ggplot2)

ggplot(dataSet,aes(job_category,salary_in_usd,fill = job_category))+
  geom_violin(show.legend = F)+
  geom_boxplot(width = 0.2,show.legend = F,outlier.color = "red",outlier.alpha = 0.3)+
  scale_y_continuous(breaks = (0:6)*10^5)+
  labs(title = "Salary Distribution Across Job Categories",x = "Job Category",y = "Salary (USD)")+
  theme(axis.title = element_text(face = "bold"),plot.title = element_text(face = "bold",size = 16))+
  coord_flip()
```
```{r}
library(ggplot2)

avgSalary = aggregate(salary_in_usd~work_year+job_category,dataSet,mean)
ggplot(avgSalary,aes(work_year,salary_in_usd,color=job_category))+
  geom_point(size=3,alpha=0.5)+
  geom_line(size = 1)+
  labs(title = "Yearly Average Salary Trends Across Job Categories",x = "Year",y = "Avg Salary(USD)")+
  theme(axis.title = element_text(face = "bold"),plot.title = element_text(face = "bold",size = 16),legend.title = element_blank())
```


```{r}

library(ggplot2)

dataSet$experience_level = as.factor(dataSet$experience_level)


expSal = aggregate(x = dataSet$salary_in_usd, by = list(dataSet$experience_level), FUN = mean)
expSal = expSal[order(c(1,3,4,2)),]

m = mean(dataSet$salary_in_usd)
dataSet$experience_level = factor(dataSet$experience_level,levels = c("EN","MI","SE","EX"))

ggplot(expSal,aes(x=Group.1,y=x))+
  geom_jitter(data = dataSet,aes(experience_level,salary_in_usd,color = experience_level),alpha = 0.5,show.legend = F)+
  geom_point(color = "#581845",size = 4)+
  geom_segment(aes(x = Group.1, xend = Group.1, y=mean(dataSet$salary_in_usd),yend = x),inherit.aes = F,size = 2,color = "#581845")+
  geom_hline(lty =2,yintercept = m)+
  coord_flip()+
  labs(title = "Salary Growth with Experience",x = "Salary (USD)",y = "Experience Level")+
  theme(axis.title = element_text(face = "bold"),plot.title = element_text(face = "bold",size = 16))


```

```{r}
library(ggplot2)
library(ggridges)

dataSet$work_year = as.factor(dataSet$work_year)


ggplot(dataSet,aes(salary_in_usd,work_year,fill= stat(x)))+
  geom_density_ridges_gradient(scale=3)+
  scale_fill_viridis_c(name = "Salary (USD)")+
  labs(title = "Salary Distribution Changes Over Time",x = "Salary (USD)",y = "Year")+
  theme(axis.title = element_text(face = "bold"),plot.title = element_text(face = "bold",size = 16))
  
```

